---
title: "Discussion 9"
author: "Cong Xu"
date: "3/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Python

```{r}
library(reticulate)
```

Tell `reticulate` to use `miniconda`.
```{r}
use_miniconda(required = TRUE)
```

### range & index

```{python}
# range(0, 4)
for i in range(4):
  print(i)

```

```{python}
for i in range(2,5):
  print(i)

```

```{python}
for i in range(5,1,-1):
  print(i)

```

```{python}
# list in python
l = [2,4,6,8,10,12]
l[0]
```

```{python}
l[0:2]
```

```{python}
l[::-1]
```

```{python}
# length of a list
len(l)
```

## Keras

Reference: https://www.tensorflow.org/tutorials/keras/classification

```{r}
library(reticulate)
library(tidyverse)
library(keras)
```

```{r}
library(rsample)
library(kernlab)
data(spam)
```

### Preparation
1. train-test split
2. transformation / standardization / scaling
3. X: np.array(n_obs, None), y: np.array(n_obs, )

```{r}
set.seed(141)
nspam <- 1813
nham <- 2788
test <- c(sample(1:nspam, floor(nspam * 0.1)), sample(nspam + 1:nham, floor(nham * 0.1)))
spam_train <- spam[-test, ]
spam_test <- spam[test, ]
```

```{r}
head(spam)
```

```{r}
X_train <- as.matrix(spam_train[, 1:57])
y_train <- 1*(spam_train[, 58] == 'spam')
X_test <- as.matrix(spam_test[, 1:57])
y_test <- 1*(spam_test[, 58] == 'spam')
```

```{python}
r.X_train.shape
```

```{python}
len(r.y_train)
```


```{python}
import numpy as np
from tensorflow import keras

X_train = r.X_train
X_test = r.X_test
y_train = keras.utils.to_categorical(r.y_train, 2)
y_test = keras.utils.to_categorical(r.y_test, 2)
```

```{python}
y_test.shape
```

### build the model
1. input layer
2. hidden layer(s)
3. output layer (goal of the task, loss function)

```{python}
model = keras.Sequential([
    keras.layers.Dense(64, activation='relu'),
    keras.layers.Dropout(0.25),
    keras.layers.Dense(2, activation="softmax")
])

```

### compile the model

```{python}
model.compile(optimizer='adam', loss=keras.losses.BinaryCrossentropy(), metrics=['accuracy'])

```

### train the model

```{python}
model.fit(X_train, y_train, epochs=10)

```

### Evaluation on testing set

```{python}
test_loss, test_acc = model.evaluate(X_test,  y_test, verbose=2)
print('Test accuracy:', test_acc)
```

### Possible improvements
1. transformation before training
2. model structure
3. hyper-parameters (number of nodes in a layer, drop-out rate, activation function, optimizer, epochs)
4. complete evaluation (in some cases accuracy is not a good metric)
