---
title: "Discussion 4"
author: "Cong Xu"
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(Rcpp)
```

# Rcpp

1. In R, avoid for/while loops. Use vectorization or 'apply'. While in Rcpp, for/while loops are efficient.
2. When defining functions in Rcpp, the code should be within `{Rcpp}`
3. In Rcpp, we must declare the types of input(s) and output(s).
4. Do not forget `;`s.
5. Import the namespace `Rcpp` for things such as `NumericVector`.
6. We need to specify the type of each variable.


## (a) whether there exists an positive element in vector `x`.

```{r}
x <- rnorm(5)
x
x>0
any(x > 0)
```

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
bool anygtC(NumericVector x){
  int n = x.size();
  for (int i = 0; i < n; i++){
    if (x[i] > 0){
      return true;
    }
  }
  return false;
}
```

```{r}
x <- runif(1e4, -1, 1)
bench::mark(
  any(x > 0),
  anygtC(x)
)
```


## (b) mean of vector `x`.

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
double meanC(NumericVector x){
  int n = x.size();
  double m = 0;
  for (int i=0; i<n; i++){
    m += x[i];
//     m = m + x[i]
  }
  return m / n;
}
```

```{r}
x <- rnorm(1e3)
mean(x)
meanC(x)
```

```{r}
bench::mark(
  mean(x),
  meanC(x)
)
```


## (c) extention, when vector `x` contains NA's

```{r}
x <- rnorm(5)
x[1] <- NA
x
mean(x)
mean(x, na.rm = TRUE)
```

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
double meanC_na(NumericVector x, bool na_rm=true){
  int n = x.size();
  double m = 0;
  int c = 0;
  for (int i=0; i<n; i++){
    if (R_IsNA(x[i])){
//   if (NumericVector::is_na(x[i])) { // another method
      if (na_rm){
        continue;
      }
      else {
        return NA_REAL;
      }
    }
    else {
      c += 1;
      m += x[i];
    }
  }
  
  if (c == 0){
    return NA_REAL;
  }
  else {
    return m / c;
  }
}
```


```{r}
x <- rnorm(1e3)
mean(x, na.rm = FALSE)
meanC_na(x, na_rm=FALSE)
```

```{r}
x[sample(1e3, 10)] <- NA
mean(x,na.rm=TRUE)
meanC_na(x, na_rm=TRUE)
```

```{r}
bench::mark(
  mean(x,na.rm=TRUE), 
  meanC_na(x, na_rm=TRUE),
  relative = TRUE
)
```


## (d) square roots for all elements in a vector

```{r}
x <- runif(5,0,1)
sqrt(x)
```

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
NumericVector sqrtC(NumericVector x){
  int n = x.size();
  int i = 0;
  NumericVector out(n);
  while (i < n){
    if (x[i] >= 0){
      out[i] = sqrt(x[i]);
    }
    else {
      out[i] = NA_REAL;
    }
    i++;
  }
  return out;
}
```

```{r}
x <- runif(10, -5, 5)
sqrt(x)
sqrtC(x)
```

```{r}
x <- runif(1e5, 0, 1)
bench::mark(
  sqrt(x),
  sqrtC(x),
  relative = TRUE
)
```


## (e) modifies (not in place) some values of a dataframe. For example, Celsius to Fahrenheit.

```{r}
df <- tibble(
    weekday = c('Mon', 'Tue', 'Wed'),
    temperature = c(20, 25, 22))
df
```

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
DataFrame modifyDataFrame(DataFrame df) {
  // access the columns
  // it is very important to clone `a` and `b`!!
  // since `clone()` does not know what `df["a"]` is, we need to specify the target type
  CharacterVector a = clone<CharacterVector>(df["weekday"]);
  NumericVector b = clone<NumericVector>(df["temperature"]);
  // make some changes
  int n = b.size();
  for (int i=0; i<n; i++){
    b[i] = 1.8*b[i] + 36;
  }
  // return a new data frame
  return DataFrame::create(_["weekday"]= a, _["temperature"]= b);
}
```

```{r}
df_f <- modifyDataFrame(df)
df_f
```

```{r}
df
```


## (f) modifies (in place) some values of a dataframe.

```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
void modifyDataFrame2(DataFrame df) {
  // casting the columns to their corresponding types
  CharacterVector a = as<CharacterVector>(df["weekday"]);
  NumericVector b = as<NumericVector>(df["temperature"]);
  // make some changes
  int n = b.size();
  for (int i=0; i<n; i++){
    b[i] = 1.8*b[i] + 36;
  }
  // we don't have to return because we are modifying in place.
}
```

```{r}
df <- tibble(
    weekday = c('Mon', 'Tue', 'Wed'),
    temperature = c(20, 25, 22))
modifyDataFrame2(df)
df
```
